---
title: "Darwin Board experiment - permutation procedures annotated/markdown"
author: "MK"
date: "2 October 2020"
output: html_document
---

Data input and preparation

```{r}
setwd("C:/Users/Mike/Documents/DB_experiments/Files for publication/Data")
REM_input<-read.csv("DB_REM_INPUT.csv",header=T)                
postime<-as.POSIXlt(REM_input$TIME,origin="2019-04-01")        #Convert TIME to POSIXct objects
REM_input$DAY<-postime$yday-90                                #Get number of days since beginning of the experiment
fac<-sapply(REM_input, is.factor)                              #Determine which input dataframe columns are factors
REM_input[fac]<-lapply(REM_input[fac],as.character)               #Convert factors to character vectors
covars<-REM_input[REM_input$TYPE %in% c("IS_GROUP_A","IS_ADULT","PARENT-OFFSPRING","PARTNER","SEX","SIBLING","at_risk"),] #Get the Eventnet covariate information only (separate from the actual data points)
non_coop<-REM_input[REM_input$TYPE %in% c("SOLO_NO_COOP","SCROUNGE","REPLACEMENT"),] #Get all of the events that were not cooperation events
coop_only<-REM_input[REM_input$TYPE %in% c("COOP_SUCCESS","COOP_FAIL"),]                    #Get just the cooperation events
```



Permutation procedure (Type 1; see Extended Data Figure 6a) - shuffle SOURCE and TARGET labels non-independently (i.e. SOURCE labels can become TARGET labels and vice versa)

```{r}
setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm1_041220")
nperm<-100   #specify number of permuted datasets to generate
nsample<-10000   #specify number of shuffles attempted
dayvec<-unique(coop_only$DAY)
s_or_t<-c("SOURCE","TARGET")
feeders<-c("EDDY","STREAM")
perc_nochange<-c()
conv_perc<-c()
outlist<-list()

for(i in 1:nperm){
  print(i)
  templist1<-list()   #a list for temporary storage for each feeder
  templist2<-list() 
  conv_check<-c()
  for(j in 1:length(dayvec)){   #for each day on which data was collected
    for(k in 1:length(feeders)){   #for each site/feeder
      dayfeed<-coop_only[coop_only$DAY==dayvec[j] & coop_only$SITE==feeders[k],]        #extract all cooperation events on selected day
      dayfeed_unperm<-dayfeed    #temporary dataset - unpermuted events for given sampling period
      if(nrow(dayfeed)>1){    #if multiple events for this day-feeder combination
        converged<-0        #initialize a code to indicate whether a valid permutation has been found (0 if not, 1 if it has been found)
        for(l in 1:nsample){                  #try to find a random shuffle that doesn't produce loops
          all_label<-c(dayfeed$SOURCE,dayfeed$TARGET)  #combine all labels into single label vector
          samp_label<-sample(all_label)          #shuffle label vector 
          s_samp<-samp_label[1:(length(samp_label)/2)]     #take the first half of the shuffled label vector as the permuted source labels
          t_samp<-samp_label[((length(samp_label)/2)+1):length(samp_label)]   #take the second half of the shuffled label vector as the permuted source labels
          loop_locs<-which(s_samp==t_samp)   #identify for which event the shuffled source label is the same as the shuffled target label (same individual cannot be both source and target for the same event)
          if(!length(loop_locs)){   #If no loops have been created by the permutation
            converged<-1      #update convergence code, as a valid permutation has been attained
            break            #break out of the for loop
          }
        }
        conv_check<-c(conv_check,converged)     #store convergence codes for post-processing sanity checks
        if(converged){               #if shuffle has produced dataset without loops 
          dayfeed$SOURCE<-s_samp      #replace original source labels in the (temporary) dataset with the source labels from the shuffle
          dayfeed$TARGET<-t_samp      #replace original target labels in the (temporary) dataset with the source labels from the shuffle
        } else {                     #loops produced, using swaps to break them
          for(m in 1:length(loop_locs)){      #for each loop to break
            repeat{
              tempsource<-s_samp[loop_locs[m]]    #get (permuted) source label for loop m
              temptarget<-t_samp[loop_locs[m]]     #get (permuted) source label for loop m
              if(tempsource!=temptarget){     #break out of repeat if source and target labels not the same
                break
              }
              other_locs<-1:length(s_samp)    #index of all events (within this sampling period)
              other_locs<-other_locs[-loop_locs[m]]   #index of all events except the loop currently being operated on
              o_loc<-sample(other_locs,1)         #select an 'other' index at random
              o_source<-s_samp[o_loc]             #get (permuted) source label at this 'other' location 
              o_target<-t_samp[o_loc]             #get (permuted) target label at this 'other' location 
              swaptype<-sample(s_or_t,1)  #select whether to swap source labels or target labels between the loop and the 'other' event
              if(swaptype=="SOURCE"){    #attempt to swap source labels
                if(o_source!=tempsource && temptarget!=o_source && temptarget!=o_target && tempsource!=o_target){   #if the swap does not result in the generation of another loop, then proceed
                  s_samp[loop_locs[m]]<-o_source   #assign 'other' source label to be new 'loop' source label
                  s_samp[o_loc]<-tempsource     #assign 'loop' source label to be new 'other' source label
                  break         #break out of repeat
                }
              } else if(swaptype=="TARGET"){   #attempt to swap target labels
                if(o_source!=tempsource && temptarget!=o_source && temptarget!=o_target && tempsource!=o_target){   #if the swap does not result in the generation of another loop, then proceed
                  t_samp[loop_locs[m]]<-o_target     #assign 'other' target label to be new 'loop' source label
                  t_samp[o_loc]<-temptarget   #assign 'loop' target label to be new 'other' source label
                  break         #break out of repeat
                }
              }
            }     #if valid swap not found for loop m, then repeat
          }    #once for loop completes, all loops have been undone through valid swaps
          dayfeed$SOURCE<-s_samp     #replace original source labels in the (temporary) dataset with the source labels from the shuffle & swap procedures
          dayfeed$TARGET<-t_samp      #replace original target labels in the (temporary) dataset with the source labels from the shuffle & swap procedures
        }
        dayfeed_unperm$ind<-seq(1,((nrow(dayfeed_unperm)*2)-1),2) #create new column for the (temporary) unpermuted dataset. Odd numbers from 1 to 2x no. of events
        dayfeed$ind<-seq(2,(nrow(dayfeed_unperm)*2),2)   #create new column for the temporary permuted dataset. Even numbers from 1 to 2x no. of events
        dayfeed$TIME<-dayfeed_unperm$TIME              #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$TYPE<-rep("NON-EVENT",nrow(dayfeed))    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$lock_bool<-dayfeed_unperm$lock_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$low_bool<-dayfeed_unperm$low_bool      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$high_bool<-dayfeed_unperm$high_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$pre_dur<-dayfeed_unperm$pre_dur        #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$post_dur<-dayfeed_unperm$post_dur      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$ANTENNA<-dayfeed_unperm$ANTENNA           #add context info from unpermuted dataset to corresponding permuted events
        pnp_df<-rbind(dayfeed_unperm,dayfeed)           #combine unpermuted and permuted datasets
        pnp_df<-pnp_df[order(pnp_df$TIME,pnp_df$ind),]    #order the combined dataframe such that each event and its corresponding non-event are adjacent, forming a dataframe that consists of alternating events and non-events
        if(k==1){                          #different storage lists for each site feeder
            templist1[[j]]<-pnp_df
          } else if(k==2){
            templist2[[j]]<-pnp_df
          }
        
      } else if(nrow(dayfeed_unperm)){    #this else if statement is evaluated if the number of events in the given sampling period is less than two. If one event has occurred, then
          dayfeed_unperm$ind<-1          #give the unpermuted event the index 1
          dayfeed$ind<-2                 #give the permuted event (which is identical to the unpermuted event, as no permutation can be performed) the index 2
          dayfeed$TYPE<-"NON-EVENT"      #label the permuted event as a non-event
          pnp_df<-rbind(dayfeed_unperm,dayfeed)   #create the combined dataframe
          if(k==1){                         #assign to storage based on feeder type
          templist1[[j]]<-pnp_df
          } else if(k==2){
          templist2[[j]]<-pnp_df
          }
        }
    }
  }
  tempdf1<-do.call(rbind,templist1)   #combine all sampling periods for the first site/feeder
  tempdf2<-do.call(rbind,templist2)    #combine all sampling periods for the second site/feeder
  bothdf<-rbind(tempdf1,tempdf2)       #combine the two all-feeder dataframes into a single overall dataframe
  temp_covar<-cbind(covars,ind=rep(NA,nrow(covars)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  temp_noncoop<-cbind(non_coop,ind=rep(NA,nrow(non_coop)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  tempout<-rbind(temp_noncoop,temp_covar,bothdf)     #combine the results of the permutation with the re-formatted other dataframe types
  tempout<-tempout[order(tempout$TIME,tempout$ind),]       #Order the final dataframe by time of event and then index (this ensures that entries that have the same time (i.e. an event and its corresponding non-event) are arranged such that the event always preceeds its corresponding non-event)
  f_name<-paste("ptest_data",toString(i),".csv",sep="")      #generate a filename for ith permuted dataset
  #write.csv(tempout,f_name)                  #save ith permuted dataset to csv file in current working directory
  
  event_df<-bothdf[bothdf$TYPE!="NON-EVENT",]
  non_df<-bothdf[bothdf$TYPE=="NON-EVENT",]
  perc_nochange<-c(perc_nochange,(sum(event_df$SOURCE==non_df$SOURCE & event_df$TARGET==non_df$TARGET)/nrow(event_df))*100)
  conv_perc<-c(conv_perc,(sum(conv_check)/length(conv_check))*100)
}

min(conv_perc)     #minimum percentage of dataset subsets (day-feeder combinations) successfully randomized without use of swaps to break generated loops for the current number of overall permutations and subset randomizations selected
max(conv_perc)     #maximum percentage of dataset subsets (day-feeder combinations) successfully randomized without use of swaps to break generated loops for the current number of overall permutations and subset randomizations selected

```

Extended Data Figure 7a:

```{r}
library(ggplot2)
plot_df<-data.frame(PNC=perc_nochange)
perc_change<-ggplot(plot_df,aes(PNC)) + geom_histogram(col="gray",fill="black",bins=10) + theme_classic() + xlab("Percentage of 'non-events' with the same labels as \n their corresponding events following permutation") + ylab("Frequency") + theme(text=element_text(family="sans",size=7)) #Plot histogram of percentage of 'non-events' that retain the same source and target labels as their corresponding observed events following permutation.

ggsave(filename="perc_change.png",plot=perc_change,type="cairo",dpi=360,width=85,height=50,units="mm")
```


Permutation procedure (Type 2; see Extended Data Figure 6b) - shuffle either SOURCE or TARGET labels independently

```{r}
setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm2_CS_061220")
#setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm2_CT_061220")

nperm<-10000   #specify number of permuted datasets to generate
nsample<-10000   #specify number of shuffles attempted
dayvec<-unique(coop_only$DAY)
feeders<-c("EDDY","STREAM")
condition_on<-"TARGET"                   #Select whether to condition on SOURCE or TARGET. Conditioning means that non-events have the same label as their respective events for the variable that is conditioned on. For example, conditioning on SOURCE means that each event/non-event pair has the same SOURCE label, so any difference between events/non-events is solely due to differences in properties of the TARGET. Conditioning is requried for investigating individual-level hypotheses with REMs.
conv_check<-c()
outlist<-list()

for(i in 1:nperm){
  print(i)
  templist1<-list()   #a list for temporary storage for each feeder
  templist2<-list() 
  for(j in 1:length(dayvec)){   #for each day on which data was collected
    for(k in 1:length(feeders)){   #for each site/feeder
      dayfeed<-coop_only[coop_only$DAY==dayvec[j] & coop_only$SITE==feeders[k],]        #extract all cooperation events on selected day
      dayfeed_unperm<-dayfeed    #temporary dataset - unpermuted events for given sampling period
      if(nrow(dayfeed)>1){    #if multiple events for this day-feeder combination
        converged<-0        #initialize a code to indicate whether a valid permutation has been found (0 if not, 1 if it has been found)
        for(l in 1:nsample){                  #try to find a random shuffle that doesn't produce loops
          if(condition_on=="SOURCE"){
            s_samp<-dayfeed[,"SOURCE"]          #source labels unchanged
            t_samp<-sample(dayfeed[,"TARGET"])    #random shuffle of target labels
          } else if(condition_on=="TARGET"){
            s_samp<-sample(dayfeed[,"SOURCE"])    #random shuffle of source labels
            t_samp<-dayfeed[,"TARGET"]           #target labels remain unchanged
          } else {
            s_samp<-sample(dayfeed[,"SOURCE"])     #random shuffle of source labels
            t_samp<-sample(dayfeed[,"TARGET"])     #random shuffle of target labels
          }
          loop_locs<-which(s_samp==t_samp)         #identify events for which source and target labels are the same (loops)
          if(!length(loop_locs)){   #If no loops have been created by the permutation
            converged<-1      #update convergence code, as a valid permutation has been attained
            break            #break out of the for loop
          }
        }
        conv_check<-c(conv_check,converged)     #store convergence codes for post-processing sanity checks
        if(converged){               #if shuffle has produced dataset without loops 
          dayfeed$SOURCE<-s_samp      #replace original source labels in the (temporary) dataset with the source labels from the shuffle
          dayfeed$TARGET<-t_samp      #replace original target labels in the (temporary) dataset with the source labels from the shuffle
        } else {                     #loops produced, using swaps to break them
          for(m in 1:length(loop_locs)){      #for each loop to break
            repeat{
              tempsource<-s_samp[loop_locs[m]]    #get (permuted) source label for loop m
              temptarget<-t_samp[loop_locs[m]]     #get (permuted) source label for loop m
              if(tempsource!=temptarget){     #break out of repeat if source and target labels not the same
                break
              }
              other_locs<-1:length(s_samp)    #index of all events (within this sampling period)
              other_locs<-other_locs[-loop_locs[m]]   #index of all events except the loop currently being operated on
              o_loc<-sample(other_locs,1)         #select an 'other' index at random
              o_source<-s_samp[o_loc]             #get (permuted) source label at this 'other' location 
              o_target<-t_samp[o_loc]             #get (permuted) target label at this 'other' location 
              if(condition_on=="TARGET"){    #attempt to swap source labels
                if(o_source!=tempsource && temptarget!=o_source && temptarget!=o_target && tempsource!=o_target){   #if the swap does not result in the generation of another loop, then proceed
                  s_samp[loop_locs[m]]<-o_source   #assign 'other' source label to be new 'loop' source label
                  s_samp[o_loc]<-tempsource     #assign 'loop' source label to be new 'other' source label
                  break         #break out of repeat
                }
              } else if(condition_on=="SOURCE"){   #attempt to swap target labels
                if(o_source!=tempsource && temptarget!=o_source && temptarget!=o_target && tempsource!=o_target){   #if the swap does not result in the generation of another loop, then proceed
                  t_samp[loop_locs[m]]<-o_target     #assign 'other' target label to be new 'loop' source label
                  t_samp[o_loc]<-temptarget   #assign 'loop' target label to be new 'other' source label
                  break         #break out of repeat
                }
              }
            }     #if valid swap not found for loop m, then repeat
          }    #once for loop completes, all loops have been undone through valid swaps
          dayfeed$SOURCE<-s_samp     #replace original source labels in the (temporary) dataset with the source labels from the shuffle & swap procedures
          dayfeed$TARGET<-t_samp      #replace original target labels in the (temporary) dataset with the source labels from the shuffle & swap procedures
        }
        dayfeed_unperm$ind<-seq(1,((nrow(dayfeed_unperm)*2)-1),2) #create new column for the (temporary) unpermuted dataset. Odd numbers from 1 to 2x no. of events
        dayfeed$ind<-seq(2,(nrow(dayfeed_unperm)*2),2)   #create new column for the temporary permuted dataset. Even numbers from 1 to 2x no. of events
        dayfeed$TIME<-dayfeed_unperm$TIME              #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$TYPE<-rep("NON-EVENT",nrow(dayfeed))    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$lock_bool<-dayfeed_unperm$lock_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$low_bool<-dayfeed_unperm$low_bool      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$high_bool<-dayfeed_unperm$high_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$pre_dur<-dayfeed_unperm$pre_dur        #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$post_dur<-dayfeed_unperm$post_dur      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$ANTENNA<-dayfeed_unperm$ANTENNA           #add context info from unpermuted dataset to corresponding permuted events
        pnp_df<-rbind(dayfeed_unperm,dayfeed)           #combine unpermuted and permuted datasets
        pnp_df<-pnp_df[order(pnp_df$TIME,pnp_df$ind),]    #order the combined dataframe such that each event and its corresponding non-event are adjacent, forming a dataframe that consists of alternating events and non-events
        if(k==1){                          #different storage lists for each site feeder
          templist1[[j]]<-pnp_df
        } else if(k==2){
          templist2[[j]]<-pnp_df
        }
      } else if(nrow(dayfeed_unperm)){    #this else if statement is evaluated if the number of events in the given sampling period is less than two. If one event has occurred, then
        dayfeed_unperm$ind<-1          #give the unpermuted event the index 1
        dayfeed$ind<-2                 #give the permuted event (which is identical to the unpermuted event, as no permutation can be performed) the index 2
        dayfeed$TYPE<-"NON-EVENT"      #label the permuted event as a non-event
        pnp_df<-rbind(dayfeed_unperm,dayfeed)   #create the combined dataframe
        if(k==1){                         #assign to storage based on feeder type
          templist1[[j]]<-pnp_df
        } else if(k==2){
          templist2[[j]]<-pnp_df
        }
      }
    }
  }
  tempdf1<-do.call(rbind,templist1)   #combine all sampling periods for the first site/feeder
  tempdf2<-do.call(rbind,templist2)    #combine all sampling periods for the second site/feeder
  bothdf<-rbind(tempdf1,tempdf2)       #combine the two all-feeder dataframes into a single overall dataframe
  temp_covar<-cbind(covars,ind=rep(NA,nrow(covars)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  temp_noncoop<-cbind(non_coop,ind=rep(NA,nrow(non_coop)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  tempout<-rbind(temp_noncoop,temp_covar,bothdf)     #combine the results of the permutation with the re-formatted other dataframe types
  tempout<-tempout[order(tempout$TIME,tempout$ind),]       #Order the final dataframe by time of event and then index (this ensures that entries that have the same time (i.e. an event and its corresponding non-event) are arranged such that the event always preceeds its corresponding non-event)
  f_name<-paste("ptest_data",toString(i),".csv",sep="")      #generate a filename for ith permuted dataset
  write.csv(tempout,f_name)                  #save ith permuted dataset to csv file in current working directory
}
```




Permutation procedure (Type 3; see Extended Data Figure 6c) - pairwise (i.e. row-wise) swaps of source and target labels. 

```{r}
setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm3_071220")
nperm<-10000  #specify number of permuted datasets to generate
nswaps<-1000         #number of pairwise source-target label swaps per day-feeder combination
dayvec<-unique(coop_only$DAY)
feeders<-c("EDDY","STREAM")

for(i in 1:nperm){
  print(i)
  templist1<-list()   #a list for temporary storage for each feeder
  templist2<-list() 
  for(j in 1:length(dayvec)){        #for each day on which data was collected
    for(k in 1:length(feeders)){        #for each site/feeder
      dayfeed<-coop_only[coop_only$DAY==dayvec[j] & coop_only$SITE==feeders[k],]        #extract all cooperation events on selected day
      dayfeed_unperm<-dayfeed
      swap<-0                #Initialize swap counter
      if(nrow(dayfeed)){
        while(swap<nswaps){             #Start looping through swaps
          ind_toswap<-sample(1:nrow(dayfeed),1)                #Select an event at random
          temp_source<-toString(dayfeed$SOURCE[ind_toswap])         #Temporary storage of the SOURCE label for the selected event
          temp_target<-toString(dayfeed$TARGET[ind_toswap])         #Temporary storage of the TARGET label for the selected event
          dayfeed$SOURCE[ind_toswap]<-temp_target               #Change the SOURCE label to the TARGET label
          dayfeed$TARGET[ind_toswap]<-temp_source               #Change the TARGET label to the SOURCE label
          swap<-swap+1                                          #Update the swap counter
        }
        dayfeed_unperm$ind<-seq(1,((nrow(dayfeed_unperm)*2)-1),2) #create new column for the (temporary) unpermuted dataset. Odd numbers from 1 to 2x no. of events
        dayfeed$ind<-seq(2,(nrow(dayfeed_unperm)*2),2)   #create new column for the temporary permuted dataset. Even numbers from 1 to 2x no. of events
        dayfeed$TIME<-dayfeed_unperm$TIME              #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$TYPE<-rep("NON-EVENT",nrow(dayfeed))    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$lock_bool<-dayfeed_unperm$lock_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$low_bool<-dayfeed_unperm$low_bool      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$high_bool<-dayfeed_unperm$high_bool    #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$pre_dur<-dayfeed_unperm$pre_dur        #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$post_dur<-dayfeed_unperm$post_dur      #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$ANTENNA<-dayfeed_unperm$ANTENNA           #add context info from unpermuted dataset to corresponding permuted events
        pnp_df<-rbind(dayfeed_unperm,dayfeed)           #combine unpermuted and permuted datasets
        pnp_df<-pnp_df[order(pnp_df$TIME,pnp_df$ind),]    #order the combined dataframe such that each event and its corresponding non-event are adjacent, forming a dataframe that consists of alternating events and non-events
        if(k==1){
          templist1[[j]]<-pnp_df
        } else if(k==2){
          templist2[[j]]<-pnp_df
        }
      }
    }
  }
  tempdf1<-do.call(rbind,templist1)   #combine all sampling periods for the first site/feeder
  tempdf2<-do.call(rbind,templist2)    #combine all sampling periods for the second site/feeder
  bothdf<-rbind(tempdf1,tempdf2)       #combine the two all-feeder dataframes into a single overall dataframe
  temp_covar<-cbind(covars,ind=rep(NA,nrow(covars)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  temp_noncoop<-cbind(non_coop,ind=rep(NA,nrow(non_coop)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  tempout<-rbind(temp_noncoop,temp_covar,bothdf)     #combine the results of the permutation with the re-formatted other dataframe types
  tempout<-tempout[order(tempout$TIME),]
  f_name<-paste("ptest_data",toString(i),".csv",sep="")      #generate a filename for ith permuted dataset
  write.csv(tempout,f_name)                  #save ith permuted dataset to csv file in current working directory
}
```






Permutation procedure (Type 4; see Extended Data Figure 6d) - shuffle edge weights or arrival latencies only (i.e. without altering the underlying network structure)

```{r}
#setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm4_091220_WEIGHT")
setwd("C:/Users/Mike/Documents/DB_experiments/ptests_perm4_101220_PREDUR")
nperm<-10000  #specify number of permuted datasets to generate
dayvec<-unique(coop_only$DAY)
feeders<-c("EDDY","STREAM")
to_shuffle<-"pre_dur"    #"WEIGHT" for event durations or "pre_dur" for arrival latency

for(i in 1:nperm){
  print(i)
  templist1<-list()   #a list for temporary storage for each feeder
  templist2<-list() 
  for(j in 1:length(dayvec)){
    for(k in 1:length(feeders)){
      dayfeed<-coop_only[coop_only$DAY==dayvec[j] & coop_only$SITE==feeders[k],]        #extract all cooperation events on selected day
      dayfeed_unperm<-dayfeed
      if(nrow(dayfeed)){    #if multiple events for this day-feeder combination
        if(to_shuffle=="WEIGHT"){
          dayfeed_unperm$WEIGHT<-dayfeed$WEIGHT<-as.character(dayfeed$WEIGHT)
          dayfeed$WEIGHT<-sample(dayfeed$WEIGHT)                 #Shuffle the edge weights
        } else if(to_shuffle=="pre_dur"){
          dayfeed_unperm$pre_dur<-dayfeed$pre_dur<-as.character(dayfeed$pre_dur)
          dayfeed$pre_dur<-sample(dayfeed$pre_dur)
        } else {
          print("Invalid edge property specified")
          break
        }
        dayfeed_unperm$ind<-seq(1,((nrow(dayfeed_unperm)*2)-1),2) #create new column for the (temporary) unpermuted dataset. Odd numbers from 1 to 2x no. of events
        dayfeed$ind<-seq(2,(nrow(dayfeed_unperm)*2),2)   #create new column for the temporary permuted dataset. Even numbers from 2 to 2x no. of events
        dayfeed$TIME<-dayfeed_unperm$TIME              #add context info from unpermuted dataset to corresponding permuted events
        dayfeed$TYPE<-rep("NON-EVENT",nrow(dayfeed))    #add context info from unpermuted dataset to corresponding permuted events
        pnp_df<-rbind(dayfeed_unperm,dayfeed)           #combine unpermuted and permuted datasets
        pnp_df<-pnp_df[order(pnp_df$TIME,pnp_df$ind),]    #order the combined dataframe such that each event and its corresponding non-event are adjacent, forming a dataframe that consists of alternating events and non-events
        if(k==1){
          templist1[[j]]<-pnp_df
        } else if(k==2){
          templist2[[j]]<-pnp_df
        }
      }
    }
  }
  tempdf1<-do.call(rbind,templist1)   #combine all sampling periods for the first site/feeder
  tempdf2<-do.call(rbind,templist2)    #combine all sampling periods for the second site/feeder
  bothdf<-rbind(tempdf1,tempdf2)       #combine the two all-feeder dataframes into a single overall dataframe
  temp_covar<-cbind(covars,ind=rep(NA,nrow(covars)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  temp_noncoop<-cbind(non_coop,ind=rep(NA,nrow(non_coop)))    #re-format the dataframes containing info that is not the target of permutation (i.e. covariates, non-cooperation events)
  tempout<-rbind(temp_noncoop,temp_covar,bothdf)     #combine the results of the permutation with the re-formatted other dataframe types
  tempout<-tempout[order(tempout$TIME),]
  f_name<-paste("ptest_data",toString(i),".csv",sep="")      #generate a filename for ith permuted dataset
  write.csv(tempout,f_name)                  #save ith permuted dataset to csv file in current working directory
}
```












